GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-03-01 paper/main.tex
update paper/main.tex: fix some typo

    Most neural architecture search methods (NASs) are time-consuming caused by 
    the fact that, during the searching, a candidate architectures must be 
    trained to evaluate how good of this architecture. This is why some of 
    training-free NAS algorithms have been proposed in recent years.

>>>>

    Most neural architecture searches (NASs) are time-consuming caused by 
    the fact that, during the searching, a candidate architecture must be 
    trained to evaluate how good of this architecture. This is why some of 
    training-free NAS algorithms have been proposed in recent years.
